Considering scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
integrate hab sel

<!-- 1: refresh why and what  -->
<!-- importance of scale in ml -->
Our results highlight the influence of social, spatial and temporal scale on
multilayer networks. For social scale, we found individuals became more
connected with increasing spatial distance threshold. Increasing land cover
resolution lead to a decrease in availability of patchy and rare habitats and,
correspondingly, lower connectivity of individuals in these habitats. Temporal
windows highlighted clear periods of increased sociality across individuals.
Finally, increasing number of observations lead to a stabilizing in network
measures. As such, scale is inherently tied to the generation  of multilayer
networks and metrics evaluating them, as well as the individual layers that make
them up.

<!-- 2: measuring sociality is powerful, fitness -->

@@

Social structure and habitat selection are intimately linked: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
novel framework for considering the influence of habitat selection and space use
on sociality.

Given that habitat data are available across a wide range of spatial scales, we
evaluated the influence of spatial resolution on multilayer network metrics. The
results indicate varied influence of increasing spatial resolution depending on
the habitat layer. As spatial resolution increased, edge overlap decreased in
forage while remaining stable in open and forest habitats (Figure
\@ref(fig:socres) D). Forage is a rare and patchy habitat on Fogo Island, as is
indicated by a decrease in the proportion of relocations in this habitat type
with increasing spatial resolution (Figure S1)<!--TODO-->. Similar to increasing
spatial distance threshold, the influence of increasing spatial resolution on
graph strength was notably different between habitat layers. Forest layers
showed little change in graph strength with increasing spatial resolution and
variation between individuals. Forage and open layers had greater individual
variation in graph strength, while forage was the sole layer to show large
responses in graph strength to increasing spatial resolution (Figure
\@ref(fig:socres) E). As such, multilayer network measures related to habitat
are explicitly dependent on spatial scale. Edge overlap can indicate if some
associations between individuals are dependent on the habitat-context
[@Battiston_2014]. If the spatial resolution of the habitat data are
insufficient to capture rare habitats, context-specific relationships between
individuals may not be captured by multilayer networks.

@@

## Spatial scale

@@

Multilayer networks can be used to explicitly consider
habitat selection and sociality across scales. Animal social systems can be
parsed by spatial contexts, defined, for example, by habitat types as in Figure
\@ref(fig:lcres). The effect of seasonality of resources can can be directly
measured by differences in habitat selection and sociality across temporal
layers as in Figure \@ref(fig:winpos) and Figure \@ref(fig:winlen). Habitat
selection can be explicitly integrated using network layers defined by selection
coefficients for individuals. These examples of explicit integrations of habitat selection
and sociality across social, spatial and temporal scales highlight the potential
for novel insights from multilayer networks.

>>>>

Our results highlight the influence of social, spatial and temporal scale on
multilayer networks. For social scale, we found individuals became more
connected with increasing spatial distance threshold. Increasing land cover
resolution lead to a decrease in availability of patchy and rare habitats and,
correspondingly, lower connectivity of individuals in these habitats. Temporal
windows highlighted clear periods of increased sociality across individuals.
Finally, increasing number of observations lead to a stabilizing in network
measures. As such, scale is inherently tied to the generation  of multilayer
networks and metrics evaluating them, as well as the individual layers that make
them up.

@@

Social structure and habitat selection are intimately related: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, the
(3) habitat patches within the home range and (4) specific resources within a
habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
selection was insufficient for capturing landscape attributes selected for by
mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
Moving past this hierarchical perspective, Mayor (2007) emphasized the
importance of considering a broad continuum of scales to reveal scale-dependent
selection and avoid the bias of predefined scales assumed to be associated with
certain behaviours.

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
(*Rangifer tarandus*) sociality differed between seasons, where social
associations were stronger in winter and contrastingly low in summer when
resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
bison*) showed stronger habitat selection in larger groups and avoidance of
predation risk was a main factor contributing to their habitat selection
[@Fortin_2009]. These examples, comparing sociality and habitat selection across
temporal or spatial contexts, are implicitly multilayer analyses.

Multilayer networks represent a novel framework for explicitly scale on the
influence of habitat selection and space use on sociality. Animal social systems
can be parsed by spatial contexts, defined, for example, by habitat types as in
Figure \@ref(fig:lcres). Given that habitat data are available across a wide
range of spatial scales, we evaluated the influence of land cover spatial
resolution on multilayer network metrics. The results indicate varied influence
of increasing spatial resolution depending on the habitat layer. As spatial
resolution increased, edge overlap decreased in forage while remaining stable in
open and forest habitats (Figure \@ref(fig:socres) D). Forage is a rare and
patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
of relocations in this habitat type with increasing spatial resolution (Figure
S1)<!--TODO-->. Similar to increasing spatial distance threshold, the influence
of increasing spatial resolution on graph strength was notably different between
habitat layers. Forest layers showed little change in graph strength with
increasing spatial resolution and variation between individuals. Forage and open
layers had greater individual variation in graph strength, while forage was the
sole layer to show large responses in graph strength to increasing spatial
resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
related to habitat are explicitly dependent on spatial scale. Edge overlap can
indicate if some associations between individuals are dependent on the
habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
are insufficient to capture rare habitats, context-specific relationships
between individuals may not be captured by multilayer networks.

The effect of seasonality of resources on sociality can be directly
measured by differences in association between individuals across time windows of resource availability. Using an ordinal multilayer network consisting of 20 discrete time windows throughout the study period, we observed periods of increased sociality
in caribou on Fogo Island (Figure \@ref(fig:temp))

<!-- These examples of explicit integrations of habitat -->
<!-- selection and sociality across social, spatial and temporal scales highlight the -->
<!-- potential for novel insights from multilayer networks. -->

@@

@@
